---
title: "Simulation - Catalog ME"
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_depth: 2
    toc_float:
      collapsed: no
      smooth_scroll: no
  pdf_document:
    toc: yes
    toc_depth: '2'
---
# Input Data
Specifications = WITH CATALOG - TOP - 10tys - all no3 - TOP414

Numer of permuations = 10000
```{r echo=FALSE, warning=FALSE, message=FALSE}
require(plyr)
library(dplyr)
library(MASS)
#library(effsize)
library(reshape2)
library(ggplot2)
library(Rmisc)
library(RColorBrewer)

source("InitSettings.R")
initSettings()

```

```{r results="hide", echo=FALSE, warning=FALSE, message=FALSE}

#Data for Operations, ME, Utilization
data <-read.csv("input/nfrRes-1-permRandom-len41-max10000-no3.txt-top414", sep=";", header=TRUE, encoding = "UTF-8", dec=".")


#data$SpecOrder <- seq(1,42)

numOfPermutations <-10000
```



#Plot values of ME for multiple and initial evolutions
```{r echo=FALSE}
#### Value Direct

###Maintainance Effort
dataForBarME <- data.frame(SpecOrder = data$SpecOrder, OurOrder = data$OurOrder, Operations = data$NumAffectedNoRTs - data$NumMatchNoRTs, Type="AddedOrModified", Match=data$NumMatchNoRTs, Perm=data$Perm)

# for (i in 0:numOfPermutations)
# {
#   filt <- filter(dataForBarME, dataForBarME$Perm==100)
#   a <- shapiro.test(filt$Operations)
#   if (a$p.value > 0.05)
#   { print(i)}
# }
# hist(filt$Operations)
# qqnorm(filt$Operations);qqline(filt$Operations)
# a$statistic

dataForBarME$SpecOrder <- factor(dataForBarME$SpecOrder, levels=seq(1,42))


mePlot <- ggplot() + geom_boxplot(data=dataForBarME, aes(x=SpecOrder, y=Operations, label = Operations, fill=Type), outlier.shape = NA)
mePlot <- mePlot + ylab("Maintenance Effort") + xlab("Projects") + labs(title=expression("A. Maintenance Effort"))

mePlot <- mePlot + scale_fill_manual(name="Considered sets of NFR templates", breaks=c("Matched", "Modified", "Added", "UnTouched", "AddedOrModified"), 
                           labels=c( "Matched","Indirectly derived", "Added", "UnTouched", "Added and Modified"), 
                           #  values=c("#0072B2", "#D55E00","#56B4E9","#E69F00"))
                           values=c("grey70", "#8bb92d", "grey55","grey65", "orange"))+ scale_x_discrete(breaks=c(1,5,10,15,20,25,30,35,40))

mePlot <- mePlot + ylim(0,80)


#mePlot <- mePlot + geom_line(data=dplyr::filter(dataForBarME, dataForBarME$Perm==1020), aes(x=SpecOrder, y=Operations, label = Operations, fill=Type, group=1), color="white")
#mePlot <- mePlot + geom_line(data=dplyr::filter(dataForBarME, dataForBarME$Perm==3717), aes(x=SpecOrder, y=Operations, label = Operations, fill=Type, group=1), color="black")



 #For saving in file - Uncomment
mePlot <- mePlot  + themeP2 + theme(
  
  legend.position="none"
  
  
  
)
mePlot

numNoRTsAddedToCatalog<- max(filter(data, data$PermID==1)$NoRTsActive) - 84
numNoRTsUncecessaryInCatalog <- 84 - top + numNoRTsAddedToCatalog
#dataForBarUtil <- data.frame(SpecOrder = data$SpecOrder, OurOrder = data$OurOrder, Operations = data$NumAffectedNoRTs , Type="MatchedModified", Perm=data$PermID)

#dataForBarUtil <- rbind(dataForBarUtil, data.frame(SpecOrder = data$SpecOrder, OurOrder = data$OurOrder,
#                                           Operations = data$NoRTsActive-numNoRTsUncecessaryInCatalog, Type="Rest", Perm=data$PermID))

#Dla full catalogu 84 templaty na początku
data$NoRTsActivePrev<-84 
data$NoRTsActivePrev<- top - numNoRTsAddedToCatalog
row <- c(top - numNoRTsAddedToCatalog, data$NoRTsActive-numNoRTsUncecessaryInCatalog)
a <- row[length(row)]
row <- row[-length(row)]

data$NoRTsActivePrev <- row
data$NoRTsActivePrev[data$SpecOrder == 1] <- top - numNoRTsAddedToCatalog #84 dla full
data$MEPerc <- (data$NumAffectedNoRTs - data$NumMatchNoRTs)/data$NoRTsActive

mePercPlot <- ggplot(data=data)
mePercPlot <- mePercPlot + geom_boxplot(aes(x=factor(data$SpecOrder, levels=seq(1,42)), y=data$MEPerc*100, label=data$MEPerc, fill="grey70"), fill=myPaletePurples[4], color="grey30", outlier.shape = NA)
#EN:
mePercPlot <- mePercPlot + themeP2 +  ylab("ME [%]") + xlab("Projects") + labs(title="A. Multiple evolutions") + theme(legend.position="no") + scale_x_discrete(breaks=c(0,10,20,30,40)) +ylim(0,60)
#PL:
#mePercPlot <- mePercPlot + themeP2 +  ylab("Pracochłonność utrzymania [%]") + xlab("Projekty") + labs(title="B. Wiele ewolucji") + theme(legend.position="no") + scale_x_discrete(breaks=c(0,10,20,30,40)) +ylim(0,60)
mePercPlot


mePercPlotFG <- ggplot(data=data)
mePercPlotFG <- mePercPlotFG + geom_boxplot(aes(x=factor(data$SpecOrder, levels=seq(1,42)), y=data$MEPerc*100, label=data$MEPerc, fill="grey70"), fill=myPaletePurples[4], color="grey30", outlier.shape = NA)
mePercPlotFG <- mePercPlotFG + themeP2 +  ylab("ME [%]") + xlab("Projects") + labs(title="A. Fine grained approach") + theme(legend.position="no") + scale_x_discrete(breaks=c(0,10,20,30,40)) +ylim(0,60)
plot(mePercPlotFG)
```

## Plot frequency analysis
### Aim of frequency analysis is to plot the percentage of the number of the catalogs (moments of simulations, frequency) that has at least ceratain value of the analyzed characteristic, e.g., what is the frequency of catalog value at 0.9? the answer will tell us how many times catalog had at least 0.9 value during multiple simulations.
```{r echo=FALSE, fig.height=10, fig.width=10}
dataMEPr <- data.frame(SpecOrder=-1, MEProb=-1, PLevel=-1)

for (i in 1:20)
{
  for (j in 35:41)
  {
    dataMEPr <- rbind(dataMEPr, data.frame(SpecOrder=j, MEProb=nrow(filter(data, data$MEPerc <= i/100 & data$SpecOrder==j))/numOfPermutations, PLevel=i/100))

}
}
dataMEPr <- filter(dataMEPr, dataMEPr$SpecOrder > -1)
dataMEPr$SpecOrder <- factor(dataMEPr$SpecOrder, levels = seq(1,42))


dataMEPrPlot <- ggplot(data=dataMEPr) + geom_point(aes(x=PLevel*100, y=MEProb, color=SpecOrder), size=3) + geom_line(aes(x=PLevel*100, y=MEProb, color=SpecOrder), size=2) + scale_color_manual(name="Number of considered projects", values=myBluePalete) + ylab("Frequency [%]") + xlab("Maintenance Effort/Catalog Size [%]") + labs(title=expression("Frequency of ME/Catalog Size")) + themeP + ylim(0,1) + guides(color=guide_legend(nrow=1))
dataMEPrPlot
#pdf(paste("./output/MESimPlotPlain-Both", ".pdf", sep=''), width = 19, height = 20)
# multiplot(plotlist = list(mePlotSimple,dataMEPrPlotSimple,mePlot, dataMEPrPlot), cols=2)
#
# dev.off()

dataMEPrPlotBar <- ggplot(data=filter(dataMEPr, dataMEPr$SpecOrder==41 & ((dataMEPr$PLevel*100)%%2)<1)) + geom_bar(aes(x=PLevel*100, y=MEProb*100, fill=SpecOrder), stat="identity", width=1) +  scale_fill_manual(name="Number of considered projects", values=myPaletePurples[3], labels=c("All projects")) + ylab("Frequency [%]") + xlab("ME [%]") + labs(title="B. Frequency analysis")  + ylim(0,100) 
dataMEPrPlotBar <- dataMEPrPlotBar + themeP2 + theme(legend.position="no")
dataMEPrPlotBar

```

## Pseudo-outlier analysis
```{r echo=FALSE, fig.height=10, fig.width=10}
dataForMEPrWithRepl<- read.csv(file=paste("input/dataForMEPrWithRepl-414-WithCatalog.csv", sep=""), sep=";", header=TRUE, encoding = "UTF-8", dec=".")

meData<- filter(dataForMEPrWithRepl, ((dataForMEPrWithRepl$PLevel*100)%%2) < 1)
meWithReplPlot <- ggplot(data=meData) + geom_point(aes(x=PLevel*100, y=MEProb*100, color=factor(Repl, levels = seq(0,5))), size=3) + geom_line(aes(x=PLevel*100, y=MEProb*100, color=factor(Repl, levels = seq(0,5)), group=Repl), size=2)
meWithReplPlot <- meWithReplPlot + ylab("Frequency(ME) [%]") + xlab("ME [%]") + labs(title="C. Pseudo-outliers analysis") 
meWithReplPlot <- meWithReplPlot + ylim(0,100) + scale_color_manual(name="#Excluded \npseudo-outliers", values=myPaletePurples, labels=c("0","3","5", "7", "9", "11"))
meWithReplPlot <- meWithReplPlot + ylim(0,100) + guides(color=guide_legend(nrow=2)) + themeP2
meWithReplPlot


```
