---
title: "Simulation - Catalog ME"
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_depth: 2
    toc_float:
      collapsed: no
      smooth_scroll: no
  pdf_document:
    toc: yes
    toc_depth: '2'
---
# Input Data
Specifications = WITH CATALOG - TOP - 10tys - all no3 - TOP414

Numer of permuations = 10000
```{r echo=FALSE, warning=FALSE, message=FALSE}
require(plyr)
library(dplyr)
library(MASS)
#library(effsize)
library(reshape2)
library(ggplot2)
library(Rmisc)
library(RColorBrewer)

source("InitSettings.R")
initSettings()

```

```{r results="hide", echo=FALSE, warning=FALSE, message=FALSE}

#Data for Operations, ME, Utilization
data <-read.csv("input/nfrRes-1-permRandom-len41-max10000-no3.txt-top414", sep=";", header=TRUE, encoding = "UTF-8", dec=".")


#data$SpecOrder <- seq(1,42)

numOfPermutations <-10000
```



#Plot values of ME for multiple and initial evolutions
```{r echo=FALSE}
####Util
numNoRTsAddedToCatalog<- max(filter(data, data$PermID==1)$NoRTsActive) - 84
numNoRTsUncecessaryInCatalog <- 84 - top + numNoRTsAddedToCatalog
dataForBarUtil <- data.frame(SpecOrder = data$SpecOrder, OurOrder = data$OurOrder, Operations = data$NumAffectedNoRTs , Type="MatchedModified", Perm=data$PermID)

dataForBarUtil <- rbind(dataForBarUtil, data.frame(SpecOrder = data$SpecOrder, OurOrder = data$OurOrder,
                                           Operations = data$NoRTsActive-numNoRTsUncecessaryInCatalog, Type="Rest", Perm=data$PermID))

#Dla full catalogu 84 templaty na początku
data$NoRTsActivePrev<-84 
data$NoRTsActivePrev<- top - numNoRTsAddedToCatalog
row <- c(top - numNoRTsAddedToCatalog, data$NoRTsActive-numNoRTsUncecessaryInCatalog)
a <- row[length(row)]
row <- row[-length(row)]

data$NoRTsActivePrev <- row
data$NoRTsActivePrev[data$SpecOrder == 1] <- top - numNoRTsAddedToCatalog #84 dla full

data$Utilization <- (data$NumAffectedNoRTs-data$NumAddedNoRT)/data$NoRTsActivePrev

#median(merged2$Utilization)

#max(data$Utilization, na.rm = TRUE)
#min(data$Utilization, na.rm = TRUE)
#mean(data$Utilization, na.rm = TRUE)
#median(data$Utilization, na.rm = TRUE)
#max(data$NumAffectedNoRTs-data$NumAddedNoRTs)
#min(data$NumAffectedNoRTs-data$NumAddedNoRTs)
#mean(data$NumAffectedNoRTs-data$NumAddedNoRTs)
#median(data$NumAffectedNoRTs-data$NumAddedNoRTs)

dataForBarUtil$SpecOrder <- factor(dataForBarUtil$SpecOrder, levels=seq(1,42))


dataUtilPr <- data.frame(SpecOrder=-1, MEProb=-1, PLevel=-1)
dataUtilPr2 <- data.frame(SpecOrder=-1, MEProb=-1, PLevel=-1)

for (i in 1:20)
{
  for (j in 35:41)
  {
    dataUtilPr <- rbind(dataUtilPr, data.frame(SpecOrder=j, MEProb=nrow(filter(data, data$Utilization <= i/100 & data$SpecOrder==j))/numOfPermutations, PLevel=i/100))
dataUtilPr2 <- rbind(dataUtilPr2, data.frame(SpecOrder=j, MEProb=nrow(filter(data, data$Utilization >= i/100 & data$SpecOrder==j))/numOfPermutations, PLevel=i/100))

}
}
dataUtilPr <- filter(dataUtilPr, dataUtilPr$SpecOrder > -1)
dataUtilPr2 <- filter(dataUtilPr2, dataUtilPr2$SpecOrder > -1)
dataUtilPr$SpecOrder <- factor(dataUtilPr$SpecOrder, levels = seq(1,42))
dataUtilPr2$SpecOrder <- factor(dataUtilPr2$SpecOrder, levels = seq(1,42))





dataForBarUtilPerc <- data.frame(SpecOrder = data$SpecOrder, OurOrder = data$OurOrder, Operations = data$Utilization , Type="UtilPerc", Perm=data$PermID)
dataForBarUtilPerc$SpecOrder <- factor(dataForBarUtilPerc$SpecOrder, levels=seq(1,42))


dataForBarUtilPerc$SpecOrder <- factor(dataForBarUtilPerc$SpecOrder, levels=seq(1,42))
utilPercPlot <- ggplot(data = dataForBarUtilPerc)
utilPercPlot <- utilPercPlot + geom_boxplot(aes(x=SpecOrder, y=Operations*100, label=Operations, fill=Type), color="grey30", outlier.shape = NA)
utilPercPlot <- utilPercPlot + scale_fill_manual(name="Type:", breaks=c("Matched", "Modified", "Added", "UnTouched", "UtilPerc"), 
                           labels=c( "Matched","Indirectly derived", "Added", "UnTouched", "UtilPerc"), 
                           #  values=c("#0072B2", "#D55E00","#56B4E9","#E69F00"))
                           values=c(myPaleteOranges[4], "#8bb92d", "grey55","grey65", "orange", "green"))
#EN
utilPercPlot <- utilPercPlot + ylab("U in [%]") + xlab("Projects") + themeP2 + scale_x_discrete(breaks=c(0,10,20,30,40)) + theme(legend.position="no") + labs(title="A. Multiple evolutions") +ylim(0,30)
#PL
#utilPercPlot <- utilPercPlot + ylab("Użycie katalogu [%]") + xlab("Projekty") + themeP2 + scale_x_discrete(breaks=c(0,10,20,30,40)) + theme(legend.position="no") + labs(title="B. Wiele ewolucji") +ylim(0,30)

utilPercPlot

utilPercPlotFG <- ggplot(data = dataForBarUtilPerc)
utilPercPlotFG <- utilPercPlotFG + geom_boxplot(aes(x=SpecOrder, y=Operations*100, label=Operations, fill=Type), color="grey30", outlier.shape = NA)
utilPercPlotFG <- utilPercPlotFG + scale_fill_manual(name="Type:", breaks=c("Matched", "Modified", "Added", "UnTouched", "UtilPerc"), 
                           labels=c( "Matched","Indirectly derived", "Added", "UnTouched", "UtilPerc"), 
                           #  values=c("#0072B2", "#D55E00","#56B4E9","#E69F00"))
                           values=c(myPaleteO[4], "#8bb92d", "grey55","grey65", "orange", "green"))

utilPercPlotFG <- utilPercPlotFG + ylab("U in [%]") + xlab("Projects") + themeP2 + scale_x_discrete(breaks=c(0,10,20,30,40)) + theme(legend.position="no") + labs(title="A. Fine grained approach") +ylim(0,30)


#For initial evolution first run other scripts
#utilPercPlotInit <- ggplot(data=dataME)
#utilPercPlotInit <- utilPercPlotInit + geom_bar(aes(x=factor(SpecOrder, levels=seq(1,42)), y=UtilPerc*100, fill=myPaleteO[5]),  stat = "identity", fill=myPaleteO[5])
#EN
#utilPercPlotInit <- utilPercPlotInit + themeP2 +  ylab("U [%]") + xlab("Projects") + labs(title="A. Initial evolution") + theme(legend.position="no") + scale_x_discrete(breaks=c(0,10,20,30,40), labels=c(0,10,20,30,40))  +ylim(0,30)
#utilPercPlotInit <- utilPercPlotInit + themeP2 +  ylab("Użycie katalogu [%]") + xlab("Projekty") + labs(title="A. Pierwsza ewolucja") + theme(legend.position="no") + scale_x_discrete(breaks=c(0,10,20,30,40), labels=c(0,10,20,30,40))  +ylim(0,30)
#plot(utilPercPlotInit)




```

## Plot frequency analysis
### Aim of frequency analysis is to plot the percentage of the number of the catalogs (moments of simulations, frequency) that has at least ceratain value of the analyzed characteristic, e.g., what is the frequency of catalog value at 0.9? the answer will tell us how many times catalog had at least 0.9 value during multiple simulations.
```{r echo=FALSE, fig.height=10, fig.width=10}
utilPercPlot402 <- ggplot(data = filter(dataUtilPr, dataUtilPr$SpecOrder==41 & ((dataUtilPr$PLevel*100)%%2) < 1))
utilPercPlot402 <- utilPercPlot402 + geom_bar(aes(x=PLevel*100, y=(MEProb)*100, fill=myPaleteOranges[4]),  stat = "identity") +  scale_fill_manual(name="Number of considered projects", values=myPaleteOranges[4], labels=c("All projects"), drop=FALSE)
utilPercPlot402 <- utilPercPlot402 +  ylim(0,100) + ylab("Frequency [%]") + xlab("U[%]") + themeP2   + labs(title="B. Frequency analysis")+ theme(legend.position="no") #+ scale_x_discrete(breaks=c(0,5,10,15,20),labels=c(0,5,10,15,20))
utilPercPlot402

```

## Pseudo-outlier analysis
```{r echo=FALSE, fig.height=10, fig.width=10}
dataForUtilWithRepl<- read.csv(file=paste("input/dataForUtilWithRepl-414-WithCatalog.csv", sep=""), sep=";", header=TRUE, encoding = "UTF-8", dec=".")

dataForUtilPlot <- filter(dataForUtilWithRepl, ((dataForUtilWithRepl$PLevel*100)%%2) < 1)
utilWithReplPlot <- ggplot(data=dataForUtilPlot) + geom_point(aes(x=PLevel*100, y=MEProb*100, color=factor(Repl, levels = seq(0,5))), size=3) + geom_line(aes(x=PLevel*100, y=MEProb*100, color=factor(Repl, levels = seq(0,5)), group=Repl), size=2) 
utilWithReplPlot <- utilWithReplPlot + scale_color_manual(name="#Excluded \npseudo-outliers", values=myPaleteOranges, labels=c("0","3","5", "7", "9", "11"))
utilWithReplPlot <- utilWithReplPlot + ylab("Frequency(U) [%]") + xlab("U [%]") + labs(title="C. Pseudo-outliers analysis") 
utilWithReplPlot <- utilWithReplPlot + ylim(0,100) + guides(color = guide_legend(nrow = 1)) + themeP2
utilWithReplPlot

```
