---
title: "Simulation - Catalog Value"
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_depth: 2
    toc_float:
      collapsed: no
      smooth_scroll: no
  pdf_document:
    toc: yes
    toc_depth: '2'
---
# Input Data
Specifications = WITH CATALOG - TOP - 10tys - all no3 - TOP414

Numer of permuations = 10000
```{r echo=FALSE, warning=FALSE, message=FALSE}
require(plyr)
library(dplyr)
library(MASS)
#library(effsize)
library(reshape2)
library(ggplot2)
library(Rmisc)
library(RColorBrewer)

source("InitSettings.R")
initSettings()

```

```{r results="hide", echo=FALSE, warning=FALSE, message=FALSE}

#Dta for Value old
#dataValue <-  read.csv("input/nortRespermRandom-len41-max10000-no3.txt", sep=";", header=TRUE, encoding = "UTF-8", dec=".", skip=20 000 000)
#dataValue <-  read.csv("input/nortRespermRandom-len41-max10000-no3.txt", sep=";", header=TRUE, encoding = "UTF-8", dec=".")

#dataValueDirect <- read.csv("input/valueRespermRandom-len41-max10000-no3.txt", sep=";", header=TRUE, encoding = "UTF-8", dec=".")

dataValueDirect <- read.csv("input/valueRes1-permRandom-len41-max10000-no3.txt-top414", sep=";", header=TRUE, encoding = "UTF-8", dec=".")
#dataValueDirect <- read.csv("input/valueRes1-perWithReplacement5-42.txt-top414", sep=";", header=TRUE, encoding = "UTF-8", dec=".")
#dataValueDirect <- filter(dataValueDirect, dataValueDirect$PermID>0)
#dataValueDirect$SpecOrder <- seq(1,42)


numOfPermutations <-10000
```



#Plot values of Catalog Value for multiple and initial evolutions
```{r echo=FALSE}
#### Value Direct

## Prepare data
dataValueDirect$SpecOrder <- factor(dataValueDirect$SpecOrder, levels=seq(1,42))

## Plot for multiple evolutions
valueDirPlot <- ggplot(data = dataValueDirect) 
valueDirPlot <- valueDirPlot + geom_boxplot(aes(x=SpecOrder, y=Value*100), fill=myBluePalete[7], outlier.shape=NA, color="grey30")
valueDirPlot <- valueDirPlot + ylim(0,100)
#EN
valueDirPlot <- valueDirPlot+ ylab("Value [%]") + xlab("Projects") + labs(title="B. Multiple evolutions")
#PL
#valueDirPlot <- valueDirPlot+ ylab("Wartość katalogu [%]") + xlab("Projekty") + labs(title="B. Wiele ewolucji")
valueDirPlot <- valueDirPlot + scale_x_discrete(breaks=c(0,10,20,30,40)) 
valueDirPlot <- valueDirPlot  + themeP2
valueDirPlot

## Plot for init evolutions
valueDirPlotInit <- ggplot(data = filter(dataValueDirect, dataValueDirect$PermID==1)) 
valueDirPlotInit <- valueDirPlotInit + geom_bar(aes(x=factor(SpecOrder, levels=seq(1,42)), y=Value*100),  stat = "identity", fill=myBluePalete[7])
#EN
valueDirPlotInit <- valueDirPlotInit + themeP2 +  ylab("Value [%]") + xlab("Projects") + labs(title="A. Initial evolution") + theme(legend.position="no")  +ylim(0,100)
#PL
#valueDirPlotInit <- valueDirPlotInit + themeP2 +  ylab("Wartość katalogu [%]") + xlab("Projekty") + labs(title="A. Pierwsza ewolucja") + theme(legend.position="no")  +ylim(0,100)
valueDirPlotInit

## Init and multiple evolutions both on the same plot
valueDirPlot_InitWithMultiple <- ggplot() 
valueDirPlot_InitWithMultiple <- valueDirPlot_InitWithMultiple + geom_boxplot(data= dataValueDirect, aes(x=SpecOrder, y=Value*100), fill=myBluePalete[7], outlier.shape=NA, color="grey30")
#valueDirPlot_InitWithMultiple <- valueDirPlot_InitWithMultiple +  geom_point(data=filter(dataValueDirect, dataValueDirect$PermID==1), aes(x=SpecOrder,  y=Value*100, size=1), color="goldenrod4") + geom_line(data=filter(dataValueDirect, dataValueDirect$PermID==1), aes(x=SpecOrder,  y=Value*100, group=1), color="goldenrod4")
valueDirPlot_InitWithMultiple <- valueDirPlot_InitWithMultiple + ylim(0,100)
#EN
valueDirPlot_InitWithMultiple <- valueDirPlot_InitWithMultiple+ ylab("Value [%]") + xlab("Projects") + labs(title="")
valueDirPlot_InitWithMultiple <- valueDirPlot_InitWithMultiple + scale_x_discrete(breaks=c(0,10,20,30,40)) 
valueDirPlot_InitWithMultiple <- valueDirPlot_InitWithMultiple  + themeP2 
valueDirPlot_InitWithMultiple


## Fine grained plot
valueDirPlotFG <- ggplot(data = dataValueDirect) 
valueDirPlotFG <- valueDirPlotFG + geom_boxplot(aes(x=SpecOrder, y=Value*100), fill=myBluePalete[7], outlier.shape=NA, color="grey30")
valueDirPlotFG <- valueDirPlotFG + ylim(0,100)
#EN
#valueDirPlotFG <- valueDirPlotFG + ylab("Value [%]") + xlab("Projects") + labs(title="A. Fine grained approach")
#PL
valueDirPlotFG <- valueDirPlotFG + ylab("Wartość katalogu [%]") + xlab("Projects") + labs(title="A. Fine grained approach")
valueDirPlotFG <- valueDirPlotFG + scale_x_discrete(breaks=c(0,10,20,30,40))  + themeP2
   valueDirPlotFG
```

## Plot frequency analysis
### Aim of frequency analysis is to plot the percentage of the number of the catalogs (moments of simulations, frequency) that has at least ceratain value of the analyzed characteristic, e.g., what is the frequency of catalog value at 0.9? the answer will tell us how many times catalog had at least 0.9 value during multiple simulations.
```{r echo=FALSE, fig.height=10, fig.width=10}
#Add new column, each for certain frequency level, and if value for this moment is at least the frequency assign 1
dataValueDirect$FreqLevel9 <- 0
dataValueDirect[dataValueDirect$Value >= 0.9,]$FreqLevel9 <- 1
dataValueDirect$FreqLevel95 <- 0
dataValueDirect[dataValueDirect$Value >= 0.95,]$FreqLevel95 <- 1
dataValueDirect$FreqLevel8 <- 0
dataValueDirect[dataValueDirect$Value >= 0.8,]$FreqLevel8 <- 1
dataValueDirect$FreqLevel85 <- 0
dataValueDirect[dataValueDirect$Value >= 0.85,]$FreqLevel85 <- 1
dataValueDirect$FreqLevel7 <- 0
dataValueDirect[dataValueDirect$Value >= 0.7,]$FreqLevel7 <- 1
dataValueDirect$FreqLevel75 <- 0
dataValueDirect[dataValueDirect$Value >= 0.75,]$FreqLevel75 <- 1
dataValueDirect$FreqLevel6 <- 0
dataValueDirect[dataValueDirect$Value >= 0.6,]$FreqLevel6 <- 1
dataValueDirect$FreqLevel65 <- 0
dataValueDirect[dataValueDirect$Value >= 0.65,]$FreqLevel65 <- 1
dataValueDirect$FreqLevel5 <- 0
dataValueDirect[dataValueDirect$Value >= 0.5,]$FreqLevel5 <- 1
dataValueDirect$FreqLevel55 <- 0
dataValueDirect[dataValueDirect$Value >= 0.55,]$FreqLevel55 <- 1

dataValueDirect$SpecOrder <- as.numeric(as.character(dataValueDirect$SpecOrder))

#Aggregating will provide the number of times the value was higher than the given freq level
dataValueDirAggr <- aggregate(dataValueDirect, by=list(dataValueDirect$SpecOrder), FUN="sum" )

#Divide by num of Permuations for percentage value (frequecy)
dataValueDirAggr$SpecOrder <- dataValueDirAggr$SpecOrder/numOfPermutations
dataValueDirAggr$FreqLevel9 <- dataValueDirAggr$FreqLevel9/numOfPermutations
dataValueDirAggr$FreqLevel95 <- dataValueDirAggr$FreqLevel95/numOfPermutations
dataValueDirAggr$FreqLevel8 <- dataValueDirAggr$FreqLevel8/numOfPermutations
dataValueDirAggr$FreqLevel85 <- dataValueDirAggr$FreqLevel85/numOfPermutations
dataValueDirAggr$FreqLevel75 <- dataValueDirAggr$FreqLevel75/numOfPermutations
dataValueDirAggr$FreqLevel65 <- dataValueDirAggr$FreqLevel65/numOfPermutations
dataValueDirAggr$FreqLevel7 <- dataValueDirAggr$FreqLevel7/numOfPermutations
dataValueDirAggr$FreqLevel6 <- dataValueDirAggr$FreqLevel6/numOfPermutations
dataValueDirAggr$FreqLevel5 <- dataValueDirAggr$FreqLevel5/numOfPermutations
dataValueDirAggr$FreqLevel55 <- dataValueDirAggr$FreqLevel55/numOfPermutations

#Filter only after 35 considered projects
dataValueDirAggr <-filter(dataValueDirAggr, dataValueDirAggr$SpecOrder >= 35)

#Prepare data frame for plots
dataForBarV <- data.frame(SpecOrder=dataValueDirAggr$SpecOrder, ValueMargin=95, PValue=dataValueDirAggr$FreqLevel95)
dataForBarV <- rbind(dataForBarV, data.frame(SpecOrder=dataValueDirAggr$SpecOrder, ValueMargin=90, PValue=dataValueDirAggr$FreqLevel9))
dataForBarV <- rbind(dataForBarV,data.frame(SpecOrder=dataValueDirAggr$SpecOrder, ValueMargin=85, PValue=dataValueDirAggr$FreqLevel85))
dataForBarV <- rbind(dataForBarV,data.frame(SpecOrder=dataValueDirAggr$SpecOrder, ValueMargin=80, PValue=dataValueDirAggr$FreqLevel8))
dataForBarV <- rbind(dataForBarV,data.frame(SpecOrder=dataValueDirAggr$SpecOrder, ValueMargin=75, PValue=dataValueDirAggr$FreqLevel75))
dataForBarV <- rbind(dataForBarV,data.frame(SpecOrder=dataValueDirAggr$SpecOrder, ValueMargin=70, PValue=dataValueDirAggr$FreqLevel7))
dataForBarV <- rbind(dataForBarV,data.frame(SpecOrder=dataValueDirAggr$SpecOrder, ValueMargin=65, PValue=dataValueDirAggr$FreqLevel65))
dataForBarV <- rbind(dataForBarV,data.frame(SpecOrder=dataValueDirAggr$SpecOrder, ValueMargin=60, PValue=dataValueDirAggr$FreqLevel6))
dataForBarV <- rbind(dataForBarV,data.frame(SpecOrder=dataValueDirAggr$SpecOrder, ValueMargin=55, PValue=dataValueDirAggr$FreqLevel55))
dataForBarV <- rbind(dataForBarV,data.frame(SpecOrder=dataValueDirAggr$SpecOrder, ValueMargin=50, PValue=dataValueDirAggr$FreqLevel5))


#Plot line
valuePlotP <- ggplot(data=dataForBarV) + geom_point(aes(x=ValueMargin, y=PValue, color=factor(dataForBarV$SpecOrder, levels=seq(1,42))), size=3) + geom_line(aes(x=ValueMargin, y=PValue, color=factor(dataForBarV$SpecOrder, levels=seq(1,42)), group=SpecOrder), size=2) + scale_color_manual(name="Num. of considered projects", values=myBluePalete)
valuePlotP <- valuePlotP + ylab("Frequency [%]") + xlab("Value [%]") + labs(title=expression("Frequency of Value ")) + ylim(0,1) + themeP + guides(color = guide_legend(nrow = 1))
valuePlotP
#pdf(paste("./output/ValuesWithProbalilityLine-Beta", ".pdf", sep=''), width = 19, height = 10)
# multiplot(plotlist = list(valuePlotPSimple, valuePlotP), cols=2)
# dev.off()


#Plot Bar
valuePlotBar <- ggplot(data=dataForBarV) + geom_bar(aes(x=ValueMargin, y=PValue*100, fill=factor(dataForBarV$SpecOrder, levels=seq(1,42))), stat="identity", position=position_dodge()) + scale_fill_manual(name="Num. of considered projects", values=myBluePalete)
valuePlotBar <- valuePlotBar + ylab("Frequency(Value) [%]") + xlab("Value [%]") + labs(title="A. Frequency of Value") + guides(fill = guide_legend(nrow = 1)) + themeP
valuePlotBar


#Plot Bar - only for the last project in the simulation - after considering 40
valuePlotBar40 <- ggplot(data=filter(dataForBarV, dataForBarV$SpecOrder==41)) + geom_bar(aes(x=ValueMargin, y=PValue*100, fill=myBluePalete[6] ), stat="identity", position=position_dodge(), width=3) + scale_fill_manual(name="#Considered \nprojects:", values=myBluePalete[6], drop=FALSE, labels=c("All projects"))

valuePlotBar40 <- valuePlotBar40 + ylab("Frequency(Value) [%]") + xlab("Value [%]") + labs(title="A. Frequency of Value") + themeP2 + theme(legend.position="no")
  #guides(fill = guide_legend(nrow = 1)) + themeP + legend("bottom", title = "ala", te)
valuePlotBar40


 #pdf(paste("./output/ValuesWithProbalilityBar-Beta", ".pdf", sep=''), width = 19, height = 10)
 #multiplot(plotlist = list(valuePlotBarSimple, valuePlotBar), cols=2)
 #dev.off()

```

## Pseudo-outlier analysis
```{r echo=FALSE, fig.height=10, fig.width=10}
dataForValueWithReplS <- read.csv(file=paste("input/dataForValueWithReplS-414-WithCatalog.csv", sep=""), sep=";", header=TRUE, encoding = "UTF-8", dec=".")
dataForValueWithReplS <- rbind(dataForValueWithReplS, data.frame(Repl=0, filter(dataForBarV, dataForBarV$SpecOrder==41 )))

dataForValueWithReplS$PValue <- dataForValueWithReplS$PValue*100



valueWithReplPlotS <- ggplot(data=dataForValueWithReplS) + geom_point(aes(x=ValueMargin, y=PValue, color=factor(Repl, levels = seq(0,5))), size=3) + geom_line(aes(x=ValueMargin, y=PValue, color=factor(Repl, levels = seq(0,5)), group=Repl),  size=2)
valueWithReplPlotS <- valueWithReplPlotS + scale_color_manual(name="#Excluded \npseudo-outliers:", values=myPaleteBlues, labels=c("0","3","5", "7", "9", "11"))
valueWithReplPlotS <- valueWithReplPlotS + ylab("Frequency(Value) [%]") + xlab("Value [%]") + labs(title=expression("C. Frequency of Value")) 
valueWithReplPlotS <- valueWithReplPlotS + ylim(0,100) + guides(color = guide_legend(nrow = 2))+ themeP2 

valueWithReplPlotS



```

```{r echo=FALSE, fig.height=10, fig.width=10}

```
